\documentclass[../PFC.tex]{subfiles}
\begin{document}

% Versión en inglés %

Only decades ago, it was really hard to comunicate people telematicaly each other, even it was awesome. Nowadays we have the opportunity to make a movement in any place and put you in contact with someone at hundred or thousands kilometers. This shows how the comunications have evolved in an incredible way. The security on these comunications is essential. Due to this, implementing cryptographic systems is vital to preserve the users and content privacy.
\*
\vspace{0.5515cm}
\\
The cryptography did not evolve slowly and during last century his progress has follow a huge rise as communication systems did. Since the most primitive methods of letter transposition to high complexity cryptological systems (cryptosystems) which take advantage of some mathematics properties to preserve a nice security level without spend a lot of resources on it (compute and storage resources). Is essential to optimize the resources to be competitive; so cryptosystems based on elliptic curves cut down noticeably the storage needs regarding others. Going in the same way, the NFC technology (\textit{Near Field Communication}), who has simplified the communication devices in a cheaper and small ones. This technology has conquer the world with a lot of applications.
%La criptografía no se ha quedado atrás y durante el último siglo su progreso ha seguido un ascenso vertiginoso al igual que el de los sistemas de comunicación. Desde los métodos más primitivos basados en cambiar una letra por la anexa; hasta complejos sistemas criptológicos (criptosistemas) que aprovechan ciertas propiedades matemáticas para preservar niveles de seguridad elevados con el gasto de menos recursos (computacionales y de almacenamiento). Optimizar los recursos es esencial para ser competitivo; y para ello la metodología de criptografía basada en curvas elípticas reduce sensiblemente la cantidad de almacenamiento necesaria respecto a otros algoritmos. De la mano va la tecnología NFC (\textit{Near Field Comunication}), la cual ha simplificado los dispositivos de comunicación en algo tan pequeño y barato que ha conquistado el planeta en forma de multitud de aplicaciones.
\*
\vspace{0.5515cm}
\\
On this Degree Final Project we will propose a solution to make secure systems with low-cost comunication devices and advanced cryptology. Furthermore, it will be shown an smartphones application which will let the user to make and use a NFC tag as high security authentication device on a made-up system.
\*
\vspace{0.5515cm}
\\
%En este Trabajo Fin de Grado (TFG a partir de ahora), comprenderemos la posibilidad de elaborar sistemas seguros con dispositivos de comunicación de bajo coste y criptología avanzada. A su vez, se implementará una aplicación para \textit{smartphones} que, gracias a algoritmos avanzados de criptografía, permitirán a un usuario crear y utilizar un \textit{tag} NFC como dispositivo de autenticación de alta seguridad en un sistema ficticio.


\end{document}